Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
checkpoint some 5.2

\subsection{Programmer effort}

%code size unzip 6.0
%2821 lines
\label{s:eval-effort}
To answer the second question, we implemented small example applications based on the above
grammars and compared code size with comparable applications that process data manually. We will
also compare a toy DNS server implemented in Nail with a similar toy DNS server provided as an
example for the Hammer parser generator. All code size measurements for C were performed by
SlocCount\cite{sloccount}.

\noindent We implemented the following applications and compare them to applications written without
Nail:

\noindent\begin{tabular}{@{}lll@{}} 
\toprule
\textbf{System} & \textbf{Nail LoC}  & \textbf{LoC w/o Nail} \\
\midrule
DNS server & 295 & 683 (Hammer parser)\\
&&  ~10.000 (DJBDNS)\\ 
DNS client & 210  & 4,615 (host) \\
\texttt{unzip} & 220 & 1600 (Info-Zip) \\
\bottomrule
\end{tabular}
%%DNS: 
\paragraph{DNS.}

>>>>

\subsection{Programmer effort}
\label{s:eval-effort}

%code size unzip 6.0
%2821 lines

To evaluate how much programmer effort is required to build an
application that uses Nail, we implemented three applications---a
DNS server, a replacement for the \cc{host} DNS client tool, and an
\cc{unzip} program---based on the above grammars, and compared code
size with comparable applications that process data manually, using
SlocCount~\cite{sloccount}.  We also compare the code size of our
DNS server to a DNS server written using the Hammer parsing framework,
although it does not fully support DNS (e.g., it lacks label compression,
among other things).  Figure~\ref{fig:effort} summarizes the results.

\XXX[nz][should we kill \cc{host}, since our replacement is nowhere
near as full-featured as the real \cc{host} or \cc{dig}?]

\begin{figure}[tb]
\centering
\begin{tabular}{llr@{~}l}
\toprule
\textbf{System}
  & \textbf{LoC w/ Nail}
  & \multicolumn{2}{c}{\textbf{LoC w/o Nail}} \\
\midrule
DNS server
  & 295
  & 683
  & (Hammer parser) \\

  &
  & 10,000
  & (DJBDNS) \\

DNS client
  & 210
  & 4,615
  & (host) \\

\cc{unzip}
  & 220
  & 1600
  & (Info-Zip) \\
\bottomrule
\end{tabular}
\caption{Comparison of code size for three applications written in Nail,
         and several existing alternative implementations.}
\label{fig:effort}
\end{figure}
